\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2023-10-10 paper.tex
Edits from yan

\begin{figure}
\centering
\includegraphics[width=\textwidth]{illustrations/simplification}
\caption{\label{fig-simplification}
Levels of ARG simplification.
In all cases the graph visualization is shown on the left
and the corresponding local trees on the right.
Nodes are coloured by the number of parents and shaded
according to the proportion of their span over which they are coalescent.
(A) A gARG simulated from a backward-time diploid Wright-Fisher
model: genome \noderef{k} has three children, and the genomes
\noderef{e} and \noderef{g} simultaneously have multiple parents and multiple children.
(B) Simplified to remove all
singly-connected graph components (e.g., diamonds such as \noderef{jlnm}).
(C) Remove nodes that never represent coalescences,
i.e.\ are unary everywhere (e.g.\ \noderef{n} and \noderef{r}).
(D) Rewrite edges to bypass nodes where they are unary in local trees.
}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{illustrations/simplification}
\caption{\label{fig-simplification}
Levels of ARG simplification.
In all cases the graph visualization is shown on the left
and the corresponding local trees on the right.
Nodes are coloured by the number of parents and shaded
according to the proportion of their span over which they are coalescent
(legend in Fig.~\ref{fig-inferred-args})
(A) A gARG simulated from a backward-time diploid Wright-Fisher
model: genome \noderef{k} has three children, and the genomes
\noderef{e} and \noderef{g} simultaneously have multiple parents and multiple children.
(B) Simplified to remove all
singly-connected graph components (e.g., diamonds such as \noderef{jlnm}).
(C) Remove nodes that never represent coalescences,
i.e.\ are unary everywhere (e.g.\ \noderef{n} and \noderef{r}).
(D) Rewrite edges to bypass nodes where they are locally unary.
}
\end{figure}
